---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/csm)](https://cran.r-project.org/package=csm)
[![Travis build status](https://travis-ci.com/UBESP-DCTV/csm.svg?token=wGyFLep97LHjNKfPGjkg&branch=master)](https://travis-ci.com/UBESP-DCTV/csm)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/csm/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/csm?branch=master)

# CSM
The goal of csm is to build a Central Statistical Monitoring (CSM) tool
that aims to sistematically check data quality of the clinical studies
managed by the Center for Clinical Trials and Biometrics (CCTB) of the
Unit of Biostatistics, Epidemiology and Public Health (UBEPH),
University of Padova, Italy.

## Installation
You can install the development version from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/csm")
```

## Feature request
If you need some more features, please open an issue on
[github](https://github.com/UBESP-DCTV/csm/issues).

## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex)
(minimal reproducible example) on
[github](https://github.com/UBESP-DCTV/csm/issues).

## Code of Conduct
Please note that the 'csm' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By
contributing to this project, you agree to abide by its terms.
